SDG contributions

### 2023-11-09 article/article.qmd
compute average specialisation factor across time for income regions
fix figure width and reduce messages

```{r load data}
library(sparklyr)
library(ggplot2)
library(patchwork)
library(dplyr)
library(arrow)
library(here)
library(tidyr)
library(forcats)
library(readr)
library(stringr)

@@

@@

```{r oa_by_sdg, fig.height=7, fig.width=9}
oa_sdg_with_gdp_per_cap %>%
  filter(sum_frac_total >= 50) %>%
  left_join(proper_countries, by = c("country" = "country_code")) %>% 
  ggplot(aes(NY.GDP.PCAP.KD, prop_oa)) +
  geom_point(aes(size = sum_frac_total, colour = region)) +
  geom_smooth(alpha = .3, show.legend = FALSE, colour = "grey30") +
  labs(x = "GDP per capita", y = "% of publications which are OA",
       colour = "World region", size = "# of publications") +
  scale_size_continuous(trans = "sqrt", labels = scales::comma) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_log10(breaks = c(1e+03, 2e+03, 5e+03, 1e+04, 2e+04, 5e+04, 1e+05),
                labels = function(x) scales::comma(x, prefix = "$")) +
  theme_bw() +
  facet_wrap(vars(fct_relevel(SDG_label, "SDG_13", after = 3)), nrow = 2) +
  theme(legend.position = c(.8, .2))
```

>>>>

```{r load data, message=FALSE}
library(sparklyr)
library(ggplot2)
library(patchwork)
library(dplyr)
library(arrow)
library(here)
library(tidyr)
library(forcats)
library(readr)
library(stringr)

@@

```{r}
income_group_specialisation %>% 
  arrange(income_group, SDG_label, year) %>% 
  rmarkdown::paged_table()
```

```{r}
income_group_specialisation %>% 
  group_by(income_group, SDG_label) %>% 
  summarise(mean_specialisation = mean(specialisation))
```

@@

```{r oa_by_sdg, fig.height=7, fig.width=10}
oa_sdg_with_gdp_per_cap %>%
  filter(sum_frac_total >= 50) %>%
  left_join(proper_countries, by = c("country" = "country_code")) %>% 
  ggplot(aes(NY.GDP.PCAP.KD, prop_oa)) +
  geom_point(aes(size = sum_frac_total, colour = region)) +
  geom_smooth(alpha = .3, show.legend = FALSE, colour = "grey30") +
  labs(x = "GDP per capita", y = "% of publications which are OA",
       colour = "World region", size = "# of publications") +
  scale_size_continuous(trans = "sqrt", labels = scales::comma) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_log10(breaks = c(1e+03, 2e+03, 5e+03, 1e+04, 2e+04, 5e+04, 1e+05),
                labels = function(x) scales::comma(x, prefix = "$")) +
  theme_bw() +
  facet_wrap(vars(fct_relevel(SDG_label, "SDG_13", after = 3)), nrow = 2) +
  theme(legend.position = c(.8, .2))
```
